Conflict Driven Evolution and Urban Development: \\ Evidence from the Holy Roman Empire\footnote{ I thank Lara Andermann, Leonie Bielefeld, Daniel Bursian, Davide Cantoni, Emilio Esguerra, Filip Milojevic, Johannes Vorbach and Matthias Weigand for helpful comments and feedback. }

### 2023-06-26 paper/paper.tex
#29 implement Daniel feedback 1/

The data on construction activity \citep{pt5} and conflict incidents \citep{pt6} both resemble lists of events. The unit of observation is the event, occurring in a specified city at a specified time point. Each entry contains additional information about the type of event and the range of uncertainty for the timing. Because I drop city-period observations with missing construction data from the sample, it is worth briefly outlining how I transform a list of events into a city-period panel of construction activity. First I group and count events that occur in the same city and period. Then I fill the observations in between the events with the value zero. Finally, I code values as missing for periods that are earlier than the first recorded event or later than the last recorded event in a city. I do not set these out-of-range values to zero because I have no way of knowing whether nothing actually happened, or whether the record simply does not cover these periods anymore.

@@

In an attempt to understand more about the effects I estimate, I use certain subsets of construction activity as the outcome in alternative specifications. There are 16 types of construction activity in the original data, which I combine into 4 facets: \textit{State construction} consists of palaces, castles, administrative and military buildings. \textit{Private construction} includes malls, economic (banks, factories, restaurants, and more) and private (residential) buildings. Lastly, \textit{construction of public goods} includes infrastructure, social, cultural, and educational buildings, memorials, gardens and parcs.\footnote
{
Churches, monasteries, clerical buildings and town halls are not included in any of the custom subsets of construction activity. They are, however, included in the "All construction" specifications.
}

@@

A key economic assumption is needed, even before the econometric ones, for these interaction terms to tell us anything about state power. It is this: the power of the state owning city $i$ is correlated with the manner in which the state acquired city $i$. In particular, I assume that conquests are more strongly positively correlated with state power than successions. Support for this assumption comes from \cite{levine2021}'s model of conflict-driven evolution. BLANK. I will discuss its validity at length later on.

>>>>

The data on construction activity \citep{pt5} and conflict incidents \citep{pt6} both resemble lists of events. The unit of observation is the event, occurring in a specified city at a specified time point. Each entry contains additional information about the type of event and the range of uncertainty for the timing. Because I drop city-period observations with missing construction data from the sample, it is worth outlining how I transform a list of events into a city-period panel of construction activity. First I group and count events that occur in the same city and period. Then I fill the observations in between the events with the value zero. Finally, I code values as missing for periods that are earlier than the first recorded event or later than the last recorded event in a city. I do not set these out-of-range values to zero because I have no way of knowing whether nothing actually happened, or whether the record simply does not cover these periods anymore.

@@

In an attempt to understand more about the effects I estimate, I use certain subsets of construction activity as the outcome in alternative specifications. There are 16 types of construction activity in the original data, which I combine into 3 facets: \textit{State construction} consists of palaces, castles, administrative and military buildings. \textit{Private construction} includes malls, economic (banks, factories, restaurants, and more) and private (residential) buildings. Lastly, \textit{construction of public goods} includes infrastructure, social, cultural, and educational buildings, memorials, gardens and parcs.\footnote
{
Churches, monasteries, clerical buildings and town halls are not included in any of the custom subsets of construction activity. They are, however, included in the "All construction" specifications.
}

@@

A key economic assumption is needed, even before the econometric ones, for these interaction terms to tell us anything about state power: the power of the state owning city $i$ is correlated with the manner in which the state acquired city $i$. In particular, I assume that conquests are more strongly positively correlated with state power than successions. Support for this assumption comes from \cite{levine2021}'s model of conflict-driven evolution. BLANK. I will discuss its validity at length later on.
